---
title: "Aids Drug"
author: "Janette Quezada"
date: "9-24-2022"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
women=filter(triUmp,gender=="F")
DrugUser=filter(triUmp,DrugUser=="yes")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aids drug (triUmpsal) is under test in clinical trials. Consider the DrugUsers, does this drug seem effective on this group?  Hint - use dplyr to obtain that sub-population with the filter command.  Next, repeat the analysis on just females, does this drug seem effective on women?

<!-- Be sure to produce Descriptive Results and Inferential Results for both groups. !-->

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed, for example sub-setting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

The questions are 1. Is the drug effective for drug users? 2. Is the vaccine effective for women?

$H_0$ There is no difference in the drug effectiveness for drug users and there is no drug effectiveness for women .

$H_A$ Says there is a difference with a new preventative aid drug called triUmpsal between drug users and females.

First we are going to separate the groups into two groups there will be two sets of analysis the drug users and the female group.


# Results

<!--Divide this section into two sub-sections:  One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

Results for women


### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe patterns, if any, that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming to or departing from what is expected by the null hypothesis !-->
```{r}
barchartGC(~infected + treatment,data=women)
barchartGC(~infected + treatment,data=women, type="percent")

```

Among the women who aids the vaccine was not effective because of a much bigger percentage that got the vaccine contracted aids than the people that got the placebo. On the graph the people that got the treatment shows they contracted aids of about 59% compared to the people that got the placebo which was less of about 49%.



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns, if any, that exist in the data as focused toward the research question!-->
```{r}
tableW <- xtabs(~infected + treatment, data=women)
rowPerc(tableW)
colPerc(tableW)
```
About 40% had the placebo vs women that took the vaccine 60%.It looks like the vaccine is more vulnerable to getting aids.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(tableW)
chisqtestGC(tableW)
fisher.test(tableW)
```


The p-value = 7.686e-05 which is lower than 0.05 so I will reject the null hypothesis.This means there is data shows that the vaccine is not effective within women if women get aids.
The vaccine makes the women more likely to get aids.



## Descriptive Results

Results for drug users


### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe patterns, if any, that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming to or departing from what is expected by the null hypothesis !-->


```{r}
barchartGC(~infected + treatment,data=DrugUser)
barchartGC(~infected + treatment,data=DrugUser, type="percent")

```

Among the drugusers who got aids the vaccine was effective because of a much smaller percentage that got the vaccine contracted aids than the people that got the placebo. On the graph the people that got the treatment shows they contracted aids of about 24% compared to the people that got the placebo which was less of about 78%.Drug users that got treated with the vaccine are less likely to get aids



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns, if any, that exist in the data as focused toward the research question!-->
```{r}
table1 <- xtabs(~infected + treatment, data=DrugUser)
rowPerc(table1)
colPerc(table1)
```
Among the people that were infected drug users show about 25% to the vaccine and 75% took the placebo this suggest that the vaccine was the drug was effective on drug users.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


The p-value = 1.242e-07 =  0.00001242 which is lower than 0.05 so I will reject the null hypothesis.This means there is data shows that the vaccine is effective within drug users.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!

Report on both Drug Users and Females.  Be sure to include the odds for both groups.
-->

Overall the Drug user when taking the treatment is less likely to get aids verses the women.The women is more likely and vulnerable to get the aids with the drug treatment.We reject the Null hypothesis because the results are lower than 0.05.
